\vfill A Survey of Web Testing Frameworks and a Workflow for Testing Javascript Applications

### 2014-05-10 Paper/paper.tex
Todo app pictures and some more stuff...

\subsection{Sample ToDo App}
In order to test out the various frameworks that we found online, we needed a small application with some functionality, but without the inherent complexity that was going to come with our evaluation application. After some searching, We decided upon a Todo application made with Express.js, Node.js, and MongoDB. \cite{ToDoAppHomePage} This application was selected because it included Node.js and had enough functionality that tests wouldn't be completely trivial while also not being overwhelming.
One of the challenges in testing that we quickly came across was the asynchronous nature of the MongoDB calls that were made in the sample app. Because of this headache, we will be discussing how the following frameworks deal with asynchronous test support as JavaScript is inherently asynchronous.
\todo{- Screenshots}
\todo{- Example Navigation}

@@

\todo{Need some sources and facts about Node.js popularity, average web application set up, etc. Can we back up our reasoning here?}

>>>>

\subsection{Sample ToDo App}
In order to test out the various frameworks that we found online, we needed a small application with some functionality, but without the inherent complexity that was going to come with our evaluation application. After some searching, We decided upon a Todo application made with Express.js, Node.js, and MongoDB. \cite{ToDoAppHomePage} Here is a brief preview of the app:

\begin{Figure}
  \centering
  \includegraphics[width=0.75\linewidth]{todo_home.png}
  \captionof{figure}{ToDo app home page, simple three-button naviagation}
\end{Figure}

\begin{Figure}
  \centering
  \includegraphics[width=0.75\linewidth]{todo_some_tasks.png}
  \captionof{figure}{ToDo app task page}
\end{Figure}

\begin{Figure}
  \centering
  \includegraphics[width=0.75\linewidth]{todo_completed.png}
  \captionof{figure}{ToDo app completed tasks page}
\end{Figure}

This application was selected because it included Node.js and had enough functionality that tests wouldn't be completely trivial while also not being overwhelming.
One of the challenges in testing that we quickly came across was the asynchronous nature of the MongoDB calls that were made in the sample app. Because of this headache, we will be discussing how the following frameworks deal with asynchronous test support as JavaScript is inherently asynchronous.

@@

Although there are multiple languages and tools available for creating a backing server, we chose Node.js because of it's wide use and because it is what we're most familiar with.

Javascript was chosen because it used in over 87\% of all websites. \cite{JSUsage} Web applications tend to keep track of users which most often constitutes the use of a database behind the scenes to store users and update them as necessary.

Many web applications use Cloud Services for a number of things, most often they're used for storage of the web content that's being hosted.
